### 2018-08-29 scripts/03-methods/README.Rmd
update readmes

# Method characterisation

@@

- Compile all the information we have about TI methods
- Group methods into sets of "tools"
- Download and process the information from the QC spread sheet (https://docs.google.com/spreadsheets/d/1Mug0yz8BebzWt8cmEW306ie645SBh_tDHwjVw4OFhlE)
- Interpret the method quality control

>>>>

# Trajectory inference methods

@@

- Compile all the information we have about TI methods
- Group methods into sets of "tools"
- Download and process the information from the QC spread sheet (https://docs.google.com/spreadsheets/d/1Mug0yz8BebzWt8cmEW306ie645SBh_tDHwjVw4OFhlE)
- Create tables and figures to interpret the methods and quality control

### 2018-08-29 scripts/README.Rmd
update readmes

```{r echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE, echo = FALSE)
```

@@

## Scripts

@@

```{r}
scripts <- read_rds(derived_file("scripts.rds", experiment_id = "12-varia/01-scripts"))

scripts %>% filter(
  level == 1
) %>%
  arrange(ix) %>%
  mutate(
    name = str_glue("[{id}](https://github.com/dynverse/dynbenchmark/tree/master/{location})"),
    order = ifelse(is.na(ix), "", ix)
  ) %>%
  select(order, subfolder = name, description = title) %>%
  knitr::kable()
```

>>>>

```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE, echo = FALSE)
```

@@

# Scripts

@@

```{r}
dynbenchmark::render_scripts_documentation()
```
